---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
```
```{r}
bent_water_chem <- read_csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_waterchem_wide.csv")
View(bent_water_chem)
```

```{r}
benth_cond_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_bentcond_08232016.csv")
benth_count_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_wide_benthic_08232016.csv")
benth_met_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_bentmet.csv")
#benth_taxa_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_benttaxa_wide_10272015.csv")
```

```{r}
View(benth_cond_L2012)
View(benth_count_L2012)
View(benth_met_L2012)
View(benth_taxa_L2012)
```
```{r}
benth_cond_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_bentcond_08232016.csv")

```

```{r}
env_chem_prof_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_profile_08232016.csv")

```

```{r}
env_chem_prof_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_profile_08232016.csv")
env_chem_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_waterchem_wide.csv")
env_algal_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_algaltoxins_08192016.csv")
env_chloro_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_chla_wide.csv")
env_atrazine_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_atrazine_08192016.csv")
phys_hab_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_phab_08232016_0.csv")
```
```{r}
View(phys_hab_L2012)
```
```{r}
env_lakes_2012_cond_cats <- read_csv("https://www.epa.gov/sites/production/files/2016-12/nla_2012_condition_categories.csv")
```


```{r}
phys_hab_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_phabmet_10202016.csv")
View(phys_hab_L2012)
```
```{r}
View(phys_hab_L2012)
```

```{r}
View(env_chem_prof_L2012)
View(env_chem_L2012)
View(env_algal_L2012)
View(env_chloro_L2012)
View(env_atrazine_L2012)
```

Under env_chem_prof_L2012 we have conductivity, depth, DO, Oxygen, pH and temperature
under benth_cond_L2012 we have a general "benthic condition" tab... there are some that are considered not assessed --> could take other parameters and try to guess what status they are?
benth_met_L2012 tells you EPT index under EPT_NIND, EPT_NTAX, EPT_PIND, EPT_PTAX
#Benthic condition they came up with 
```{r}
bent_cond_select <- benth_cond_L2012 %>% 
  dplyr::select(UID, SITE_ID, BENT_COND, RICH_PT, TOLR_PT, DIVS_PT) 

bent_cond_select

```

#Selecting important columns for benthic data
library(tidyverse)

```{r}
benth_cond_filtered <- benth_cond_L2012 %>%
  dplyr::select(SITE_ID, BENT_COND, RICH_PT, TOLR_PT, DIVS_PT) %>% 
  filter(!is.na(RICH_PT))
#filtered TOTALNIND under 100 for statistical significance?
View(benth_cond_filtered)
```

```{r}
env_atrazine_L2012_filtered <- env_atrazine_L2012 %>% 
  dplyr::select(SITE_ID, ATRAZINE_RESULT)

```

```{r}
env_lakes_2012_cond_cats_selected <- env_lakes_2012_cond_cats %>% 
  dplyr::select(SITE_ID, LAKE_ORIGIN12, MISS_BASIN, OWN_TYPE, SIZE_CLASS, NTL_COND, ACID_CLS, TURB_COND, MICX_DETECT, SEDHG_MTH_TOP_COND, ZOOP_COND, DIS_O2_CLS, TROPHIC_STATE, MICX_REC)
```


```{r}
selected_benth_met_L2012 <- benth_met_L2012 %>% 
  dplyr::select( SITE_ID, YEAR, EPT_PIND, EPT_PTAX, EPT_NTAX, WTD_TV)
View(selected_benth_met_L2012)
```

```{r}
env_chem_prof_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_profile_08232016.csv") 
```
```{r}
selected_env_chem_prof_L2012 <- env_chem_prof_L2012 %>%
  dplyr::select(UID, SITE_ID, STATE, CONDUCTIVITY, DEPTH, OXYGEN, PH, TEMPERATURE)
```

```{r}
selected_phys_hab_L2012 <- phys_hab_L2012 %>% 
  dplyr::select(SITE_ID, HIIAGCIRCA_RIP)
View(selected_phys_hab_L2012)
```


```{r}
#filtered <- selected_env_chem_prof_L2012 %>%
  #SITE_ID[SITE_ID == ""] <- NA
selected_env_chem_prof_L2012new <- selected_env_chem_prof_L2012 %>% 
  mutate(SITE_ID = ifelse((SITE_ID) == "", NA, SITE_ID)) %>% 
  filter(!is.na(SITE_ID)) %>% 
  filter(!is.na(CONDUCTIVITY) & !is.na(DEPTH) & !is.na(OXYGEN) & !is.na(PH) & !is.na(TEMPERATURE)) %>% 
  group_by(SITE_ID, STATE) %>% 
  summarize(Conductivity = mean(CONDUCTIVITY),
            Depth = mean(DEPTH),
            Oxygen = mean(OXYGEN),
            pH = mean(PH), 
            Temperature = mean(TEMPERATURE))

View(selected_env_chem_prof_L2012new)
```


```{r}
#merged <- merge(selected_benth_met_L2012, selected_env_chem_prof_L2012new, by = "SITE_ID")

merged <- right_join(selected_env_chem_prof_L2012new, selected_benth_met_L2012, by = "SITE_ID")

merged <- right_join(merged, benth_cond_filtered, by = "SITE_ID")

merged <- right_join(merged, env_atrazine_L2012_filtered, by = "SITE_ID")

merged <- right_join(merged, env_lakes_2012_cond_cats_selected, by = "SITE_ID")
merged <- right_join(merged, selected_phys_hab_L2012, by = "SITE_ID")
merged <- merged %>%
  filter(!is.na(STATE))
View(merged)

###update at 2:46pm 2018-11-27
merged <- merged %>%
  select(Conductivity, Depth, pH, Temperature, Oxygen, RICH_PT, SITE_ID)


```
```{r}


merged <- merged %>%
  mutate(Temperature = ifelse(Temperature > 50, NA, Temperature)) %>% 
  filter(!is.na(Temperature))

merged %>%
  ggplot(aes(x = Temperature, y = RICH_PT)) +
  geom_point()
```

```{r}
merged <- merged %>%
  filter(



```



```{r}
library(multcomp)
merged$BENT_COND <- as.factor(merged$BENT_COND)
summary(lm(pH ~ BENT_COND, data = merged))
result <- lm(pH ~ BENT_COND, data = merged)
postHocs<-glht(result, linfct = mcp(BENT_COND = "Tukey"))
#summary function gives results of multiple comparisons
summary(postHocs)
```



model selection and dredge
```{r}
install.packages("MuMIn")
library(MuMIn)
```

```{r}
#library(MuMIn)
model_sat <- lm(RICH_PT ~ logged_conductivity*logged_depth*Oxygen +logged_conductivity*logged_depth*pH + logged_conductivity*logged_depth*Temperature + logged_conductivity*Oxygen*pH + logged_conductivity*Oxygen*Temperature + logged_conductivity*pH*Temperature + logged_depth*Oxygen*pH + logged_depth*pH*Temperature + Oxygen*pH*Temperature + logged_depth*Oxygen*Temperature, data = merged)

Model_dredge <- dredge(model_sat, beta = F, evaluate = T, rank = AIC)

options(na.action = "na.omit")

summary(Model_dredge)
View(Model_dredge)

logged_depth


#Conductivity, depth, oxygen, pH, temperature 


#options(na.action = "na.omit")

#stepAIC_mod <- stepAIC(model_sat, direction = "backward")
#?stepAIC
#stepAIC_mod

#options(na.action = "na.fail")



#read up on step AIC and how to interpret it
#will end up with a reuduced model and then put that one into dredge 
#if still have too many go back to drawing board and try to figure out what matters most
#do not include anything over a 3 way interaction, because anything more is too complex 


#if you have x:y:z you need to have x:y, x:z, y:z, z, y, x


#if you think the interaction between x and y are important than you need to include x and y seperately too

#look into results of AIC

#start with a model that does not include any interactions above a 3 way because it will get too complicated 



```

```{r}
top_model <- get.models(Model_dredge, subset = delta <= 2)
top_model

summary(top_model)


```

```{r}
summary(model.avg(top_model))

```

```{r}
model_selected <- lm(RICH_PT ~ Depth + pH + Temperature + Oxygen:pH  + Oxygen:Temperature + pH:Temperature + Depth:Oxygen:pH + Depth:Oxygen:Temperature + Oxygen:pH:Temperature, data = merged)
plot(model_selected)

summary(model_selected)


#report table of model and bold significant one


```

```{r}
merged %>% 
  ggplot(aes(x = log10(Depth))) +
  geom_histogram()

merged %>%
  ggplot(aes(x = pH)) +
  geom_histogram()

merged %>% 
  ggplot(aes(x = Oxygen)) +
  geom_histogram()

merged %>% 
  ggplot(aes(x = log10(Conductivity))) +
  geom_histogram()


#pH and oxygen are totally fine, depth is left skewed (should we log it), conductivity def needs to be logged
```


```{r}
install.packages("scatterplot3d", dependencies = TRUE)
library(scatterplot3d)
#scatterplot3d(x = data$x, y = data$y, z = data$z)



scatterplot3d(x = merged$Oxygen, y = merged$RICH_PT, z = merged$PH, highlight.3d=TRUE, )
```





##References for future citations
https://link.springer.com/content/pdf/10.1186%2F2052-336X-12-30.pdf
* The most important water quality parameters in terms of impact on aquatic ecosystems include temperature, salinity, acidity, Total Dissolved Solids (TDS), pH, DO and BOD5.* 
