---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
```

```{r}
benth_cond_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_bentcond_08232016.csv")
benth_count_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_wide_benthic_08232016.csv")
benth_met_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_bentmet.csv")
#benth_taxa_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_benttaxa_wide_10272015.csv")
```

```{r}
View(benth_cond_L2012)
View(benth_count_L2012)
View(benth_met_L2012)
View(benth_taxa_L2012)
```
```{r}
benth_cond_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_bentcond_08232016.csv")

```


```{r}
env_chem_prof_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_profile_08232016.csv")
env_chem_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_waterchem_wide.csv")
env_algal_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_algaltoxins_08192016.csv")
env_chloro_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_chla_wide.csv")
env_atrazine_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-11/nla2012_atrazine_08192016.csv")
phys_hab_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_phab_08232016_0.csv")
```

```{r}
phys_hab_L2012 <- read.csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_phab_08232016_0.csv")
View(phys_hab_L2012)
```

```{r}
View(env_chem_prof_L2012)
View(env_chem_L2012)
View(env_algal_L2012)
View(env_chloro_L2012)
View(env_atrazine_L2012)
```

Under env_chem_prof_L2012 we have conductivity, depth, DO, Oxygen, pH and temperature
under benth_cond_L2012 we have a general "benthic condition" tab... there are some that are considered not assessed --> could take other parameters and try to guess what status they are?
benth_met_L2012 tells you EPT index under EPT_NIND, EPT_NTAX, EPT_PIND, EPT_PTAX
#Benthic condition they came up with 
```{r}
bent_cond_select <- benth_cond_L2012 %>% 
  select(UID, SITE_ID, BENT_COND)

bent_cond_select

```

#Selecting important columns for benthic data
```{r}

```

```{r}
benth_cond_filtered <- benth_cond_L2012 %>%
  select(SITE_ID, BENT_COND)
#filtered TOTALNIND under 100 for statistical significance?
View(benth_cond_filtered)
```

```{r}
selected_benth_met_L2012 <- benth_met_L2012 %>% 
  select(UID, SITE_ID, YEAR, EPT_PIND, EPT_PTAX)
View(selected_benth_met_L2012)
```

```{r}
env_chem_prof_L2012 <- read_csv("https://www.epa.gov/sites/production/files/2016-12/nla2012_wide_profile_08232016.csv") 
```

```{r}
selected_env_chem_prof_L2012 <- env_chem_prof_L2012 %>%
  dplyr::select(UID, SITE_ID, STATE, CONDUCTIVITY, DEPTH, OXYGEN, PH, TEMPERATURE)
```

```{r}
#filtered <- selected_env_chem_prof_L2012 %>%
  #SITE_ID[SITE_ID == ""] <- NA
selected_env_chem_prof_L2012new <- selected_env_chem_prof_L2012 %>% 
  mutate(SITE_ID = ifelse((SITE_ID) == "", NA, SITE_ID)) %>% 
  filter(!is.na(SITE_ID)) %>% 
  filter(!is.na(CONDUCTIVITY) & !is.na(DEPTH) & !is.na(OXYGEN) & !is.na(PH) & !is.na(TEMPERATURE)) %>% 
  group_by(SITE_ID, STATE) %>% 
  summarize(Conductivity = mean(CONDUCTIVITY),
            Depth = mean(DEPTH),
            Oxygen = mean(OXYGEN),
            pH = mean(PH), 
            Temperature = mean(TEMPERATURE))

View(selected_env_chem_prof_L2012new)
```


```{r}
#merged <- merge(selected_benth_met_L2012, selected_env_chem_prof_L2012new, by = "SITE_ID")

merged <- right_join(selected_env_chem_prof_L2012new, selected_benth_met_L2012, by = "SITE_ID")
merged <- merged %>%
  filter(!is.na(STATE))
View(merged)

```
